A Study on Neural Models for Target-Based Computer-Assisted Musical Orchestration

### 2021-04-08 csmc_mume_2020/paper/JCMS_2021/paper.tex
First round of edits, adjusting figures

% first the title is needed
\title{change}

% a short form should be given in case it is too long for the running head
\titlerunning{change}

@@

In this paper we do preliminary experiments with two deep architectures: a convolutional neural network (CNN) with a long short-term memory (LSTM) unit in the middle and \emph{ResNet}, a well known residual architecture that already yielded good results for image classification \cite{He15}. We chose to use a CNN because of its success in audio classification \cite{Hershey17} and we decided to include an LSTM unit in it because of its ability to learn long term dependencies in data \cite{Hochreiter97}, which is important given the temporal nature of audio.

After training these models on varying combinations of 10 instruments, we used them for orchestration. More specifically, we orchestrated 15 target sounds by feeding them to the networks and synthesizing a solution from the most likely samples output from the system. We then compared our orchestrations to Orchidea's solutions for the same targets, through both qualitative and quantitative means. For quantitative comparison, we computed a specific distance metric on the FFTs of the target and solution, comparing the distance between Orchidea's solution and the target and our model's solution and the target.

Next sections will be as follows: section \ref{sec:models} will describe the dataset we used for experiments and the models we trained as classifiers, showing the classification results. Sections \ref{sec:orchestration} and \ref{sec:conclusions} will present, respectively, the results of orchestration experiments using the trained models and the conclusions of our preliminary study on neural approaches for target-based computer-assisted orchestration.

The codebase for this paper and some audio examples can be found at: \url{https://github.com/dzluke/DeepOrchestration}.

%In this paper we perform preliminary experiments with two deep architectures: a convolutional neural network (CNN) with a long short-term memory (LSTM) unit and \emph{ResNet}, a well known residual architecture that already yielded good results for image classification \cite{He15}. We chose to use a CNN because of its success in audio classification \cite{Hershey17} and we decided to include an LSTM unit in it because of its ability to learn long term dependencies in data \cite{Hochreiter97}, which is important given the temporal nature of audio. The codebase for this paper can be found at: \url{https://github.com/dzluke/DeepOrchestration}.

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.22]{../ISMIR_2020/figs/CNN_LSTM_diagram.png}
	\caption{Diagram of the CNN with LSTM architecture. \label{cnn_lstm}}
\end{figure}

@@

In this paper, we model assisted orchestration as a classification problem. The general methodology is as follows:
\begin{enumerate}
\item we train specific models to classify the instruments present in combinations of sounds from a database of instrument notes, up to ten simultaneous instruments;
\item we then pick the best classifier and we feed into it an unknown sound to be classified;
\item since the output of the classifier will be in the form of the probability that specific instruments are present in the sound, we use this information to synthesize an orchestration for the target sound;
\item finally, we evaluate the generated orchestration against state-of-the-art systems for computer-assisted orchestrations.
\end{enumerate}

@@

@@

Three baseline classifiers have been trained to recognize either the instrument only for a total of 12 classes (the instruments in TinySOL) or the pair instrument-pitch \emph{class} (a pitch class is the pitch of a note without the corresponding octave, e.g. C, D\#, G, etc.) for a total of 25 classes (we will classifiy combinations of 2 instruments for 12 pitch classes each, plus one extra \emph{trash} class, see section \ref{sec:baseline}).

Two neural classifiers, instead, have been trained on the more complex problem of recognizing instrument-pitch pairs, for a total of 424 classes (i.e. the neural classifiers would classify instruments and pitches with respective octaves, hence 12 instruments for 12 pitch classes and three dynamics; note that not all the samples in TinySOL have all dynamics). We want to point out, however, that this is still a simplified problem compared to assisted orchestration. Even in the case of instrument-pitch pair classification, indeed, we would miss the dynamics of the note. To cope with this problem, in the orchestration phase, we quantize the probability functions generated by the models. When a network is given a target sound as input, it will attempt to apply the same classification rules, outputting a vector of the probabilities of each sample being in the target sound. Since the classes only encode instrument-pitch pairs and since we also need the dynamics, we quantize the probability function generated by the network into three echelons coresponding, respectively, to the dynamic levels \emph{pianissimo}, \emph{mezzoforte} and \emph{fortissimo} (see section \ref{sec:orchestration}). By taking the instruments and pitches that have the highest probability and by using quantized probabilities to retrieve dynamics, a full orchestrated solution can be created.  Figure \ref{fig:method} illustrates the described ideas.

@@

To create the input data for training the classifiers, we used the \emph{TinySOL} database. TinySOL is a subset of the Studio On Line (SOL) database created by IRCAM \cite{Cella2020b}. TinySOL contains 1,529 samples from 12 instruments. The instruments come from different orchestral families: strings, woodwinds, and brass. Each sample is one instrument playing a single note in the \emph{ordinario} playing style, with one of three dynamics: \textit{pp}, \textit{mf}, or \textit{ff} (for example \texttt{Flute-C4-pp} or \texttt{Clarinet-D5-mf}).

The instruments and ranges over which they were recorded are summarized in table \ref{tab:ranges}.

For a given number of instruments $N$, each input to our models is a combination of $N$ TinySOL samples chosen among an orchestra of 10 instruments. The data is generated in the following way:

\begin{itemize}
\item $N$ random TinySOL samples are selected, leading to a variety of instruments, pitches, and dynamics; we did not allow the same instrument to be chosen more than three times in order to ensure variety in the mixtures;
\item the chosen samples are combined to be played simultaneously, and the resulting sum is normalized by the number of instruments;
\item the Mel frequency cepstral coefficients (MFCCs) and the Mel spectrogram of the mixture are computed to be used as the input features for the baseline classifiers and the neural classifiers respectively.
\end{itemize}

For a given number of instruments $N$, each input to our model is a combination of $N$ TinySOL samples chosen among an orchestra of 10 instruments. The data is generated by selecting $N$ random TinySOL samples, leading to a variety of instruments, pitches, and dynamics; we did not allow the same instrument to be chosen more than three times in order to ensure variety in the mixtures. Then the chosen samples are combined to be played simultaneously and normalized by the number of instruments. The resulting combination has a sample rate of $44100$Hz and is padded or trimmed to be exactly 4 seconds long. The Mel spectrogram of the mixture is computed using an FFT hop length of 2048 samples (the window of each FFT is $46$ms wide) and 128 Mel bins. Therefore, the Mel features fed to the model are matrices of size $128\times 345$.

The choice of using the Mel spectrogram as input features for classification models is common in music information retrieval \cite{McKinney2003} and can be considered to be an appropriate representation of sound and musical signals. The Mel spectrogram is generated using an FFT hop length of 2048 samples (the window of each FFT was $46$ms wide), and a number of Mel bins equal to 128. Therefore, the Mel features fed to the model were matrices of size $128\times 345$. We used the Librosa package in Python to compute the features; more details on the exact computations can be found in \cite{mcfee15}. The choice of the hop length was made by doing a compromise between the amount of information extracted by each FFT window, and the ability to capture changes in the dynamic, assuming that no change faster than $10$ms would be allowed.
Such setup proved to be successful in \cite{Salamon17}.

\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
\textbf{Instrument} & \textbf{Abbreviation} & \textbf{Range} \\
\hline
Violin & Vn & G3-E7\\
Cello & Vc & C2-C6\\
Viola & Va & C3-C7\\
Trumpet C & TpC & F\#3-C6\\
Trombone & Tbn & A\#0;A\#1-C5\\
Oboe & Ob & A\#3-A6\\
Horn & Hn & G1-F5\\
Flute & Fl & B3-D7\\
Clarinet Bb & ClBb & D3-G6\\
Contrabass & Cb & E1-C5\\
Bass Tuba & BTb & F\#1-F4\\
Bassoon & Bn & A\#1-D\#5\\
\hline
\end{tabular}
\caption{Table showing the pitch ranges present in the TinySOL database.\label{tab:ranges}}
\end{center}
\end{table}

@@

In order to get a better sense on the complexity of the problem, we tested three baseline classifiers: support vector machine (SVM), random forest (RF), and K-nearest neighbours (KNN). We used the implementations provided in the \emph{scikit-learn }library for Python \cite{scikit-learn}. More specifically, for SVM we used a non-linear RBF kernel and for RF we set the maximum depth of each tree to be 15.  All of the baseline experiments used 50,000 generated samples with a train-test split of 60/40. Each sample was made by a combination of one to ten instruments and was four seconds in length.
In this case, differently from the neural models, the features used are the MFCCs of the resulting combination; we chose to use MFCCs for this setting, instead of the Mel spectrogram, to have a lower number of features, that is more manageable by parametric classifiers. We found SVM to have the highest accuracy of the three classifiers across all experiments.

The complete problem of classification of the pairs instrument-pitch has 424 total classes. This problem is very hard for parametric classifiers, so we initially switched to the simpler problem of classifying only the instruments and not the pitch. This had the benefit of both reducing the number of classes and increasing the number of samples per class. We found that SVM was able to very accurately identify the instrument given an input that had only one instrument present; for this case the accuracy was 99.8\%. However, as soon as multiple instruments were present in the input, the accuracy dropped significantly. With two instruments, accuracy was 55.4\%, with three it was 19.6\%. KNN performed significantly worse than SVM, so we did not attempt any further testing with it.

@@

We then performed this same experiment with three instruments having their pitch class identified. Flute, Oboe, and Violin reached an accuracy of 11.1\%, and Bass Tuba, Trumpet, and Trombone was 0.5\%. As we increased the number of instruments whose pitch classes was being identified, the accuracy continued to drop.Indeed, for classifying the pitch class of four instruments (Oboe, French Horn, Violin, and Flute) the accuracy was 2.7\%.

This was still a simplified version of the problem, as we were identifying only the pitch class of a few instruments. However, the parametric classifiers were unable to achieve accurate results as the number of instruments increased. Therefore, we did not attempt, with parametric classifiers, the full setting of the problem in which individual pitches are classified for all instruments.

@@

Following the first three convolutional layers, there is an LSTM layer which outputs 32 matrices. After the LSTM layer, there is a final convolutional layer yielding a tensor of dimensions $32\times 8 \times 21$. We flatten the outputs and feed them into a fully connected layer with Dropout, then another another fully connected layer. Finally, the sigmoid function is applied to the final layer. Since each class is independent, we are able to take the sigmoid activation and use binary classification for each class. %The model architecture is shown in Figure \ref{cnn_lstm}.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{../ISMIR_2020/figs/Acc_vs_N_CNN.png}
\caption{Best overall accuracy and for each instrument obtained by the CNN with LSTM depending on the number of instruments in the combinations. \label{best_acc_cnn}}
\end{center}
\end{figure}

\begin{figure}
  \center{
  \includegraphics[scale=0.4]{../ISMIR_2020/figs/CNN_vs_ResNet.png}}
  \caption{Best overall accuracy for CNN with LSTM (50 epochs, 200k samples per epoch) and ResNet (20 epochs, 400k samples per epoch) depending on the number of instruments in the combinations used for training. \label{cnn_vs_resnet}}
\end{figure}

@@

\begin{figure}
  \centering
  \begin{subfigure}{.52\textwidth}
    \centering
    \includegraphics[width=0.9\linewidth]{../ISMIR_2020/figs/Acc_vs_N_CNN.png}
    \caption{CNN with LSTM}
    \label{best_acc_cnn}
  \end{subfigure}%
  \begin{subfigure}{.52\textwidth}
    \centering
    \includegraphics[width=0.9\linewidth]{../ISMIR_2020/figs/Acc_vs_N_ResNet.png}
    \caption{ResNet}
    \label{best_acc_resnet}
  \end{subfigure}
  \caption{Best overall accuracy and for each instrument obtained by the CNN with LSTM and the ResNet depending on the number of instruments in the combinations}
  \end{figure}

@@

In order to test our models for orchestration, we used 15 targets from the Orchidea distribution. These targets represent a variety of signal types but are mostly static, in the sense that the harmonic average across time is a good representation of the sample. Some of the targets were made of instrumental samples: a sum of oboe and bassoon notes, single bassoon and bass clarinet notes, two multiphonics of bassoon and two symphonic chords. The other targets there are: the recordings of two bells, of a car horn, of a gong, of a screaming voice, of a wind harp, of the attack of a brass instrument and the recording of a boat docking.

In order to test our models for orchestration, we used 15 targets from the Orchidea distribution. These targets represent a variety of signal types but are mostly static, in the sense that they do not change sensibly over time. Some of the targets were made of instrumental samples and chords, others are bells or gongs, and some do not feature any musical instruments

@@

In order to have a fairer comparison, we did not allow Orchidea to use any of the advanced features: we did not apply any symbolic constraints or harmonic analysis and we forced it forced to use all 10 instruments in each solution. This creates a more fair comparison, since our models are unable to create constrained or sparse solutions.

@@

We calculated the distance between the target samples and our orchestrated solutions. We then orchestrated the same targets with Orchidea and calculated the distance for Orchidea's solutions. A comparison of these results is in Table \ref{orch_eval}.

@@

A comparison of distances between our solutions and targets and Orchidea's solutions and targets is in Table \ref{orch_eval}. While our model is not able to outperform Orchidea, it shows consistent results. We find that the CNN and ResNet give similar accuracies during training, but perform differently when tasked with orchestrating targets. Overall, CNN seems to better emulate the timbre in its orchestrations, where ResNet is better for recreating the harmonic content of the target. You can listen to the targets and orchestrated solutions from Orchidea, ResNet, and the CNN with LSTM at \url{https://dzluke.github.io/DeepOrchestration/}.

>>>>

% first the title is needed
\title{A Study on Neural Models for Target-Based Computer-Assisted Musical Orchestration}

% a short form should be given in case it is too long for the running head
\titlerunning{Neural Models for Target-Based Computer-Assisted Musical Orchestration}

@@

We perform preliminary experiments with two deep architectures: a convolutional neural network (CNN) with a long short-term memory (LSTM) unit in the middle and \emph{ResNet}, a well known residual architecture that already yielded good results for image classification \cite{He15}. We choose to use a CNN because of its success in audio classification \cite{Hershey17} and include an LSTM unit in it because of its ability to learn long term dependencies in data \cite{Hochreiter97}, which is important given the temporal nature of audio.

After training these models on varying combinations of 10 instruments, we use perform orchestration by feeding target sounds to the networks and synthesizing a solution from the most likely samples output from the system. We then compare our orchestrations to Orchidea's solutions for the same targets, through both qualitative and quantitative means. For quantitative comparison, we compute a specific distance metric on the amplitude spectrums of the target and solution, comparing the distance between Orchidea's solution to the target and our model's solution to the target.

The next sections will be as follows: section \ref{sec:models} will describe the dataset we used for experiments and the models we trained as classifiers, showing the classification results. Sections \ref{sec:orchestration} and \ref{sec:conclusions} will present, respectively, the results of orchestration experiments using the trained models and the conclusions of our preliminary study on neural approaches for target-based computer-assisted orchestration.

This paper is an extended version of a paper by the same title in \textit{The 2020 Joint Conference on AI Music Creativity} \cite{Cella2020c}. This version includes additional figures and extended information on our baseline testing and orchestration process. The codebase for this paper can be found at \url{https://github.com/dzluke/DeepOrchestration} and you can listen to audio examples at \url{https://dzluke.github.io/DeepOrchestration/}.

@@

@@

In this paper, we model assisted orchestration as a classification problem. The general methodology is as follows:

\begin{enumerate}
\item we train specific models to classify the instruments present in combinations of sounds from a database of instrument notes, up to ten simultaneous instruments;
\item we then pick the best classifier and we feed into it an unknown sound to be classified;
\item since the output of the classifier will be in the form of the probability that specific instruments-note pairs are present in the sound, we use this information to synthesize an orchestration for the target sound;
\item finally, we evaluate the generated orchestration against state-of-the-art systems for computer-assisted orchestrations.
\end{enumerate}

@@

As described in Sec. \ref{sec:baseline}, three baseline classifiers have been trained on simplified versions of our problem. They have been trained to either identifying only the instruments present, or the instruments and pitch classes present.

@@

Two neural classifiers have been trained on the more complex problem of recognizing instrument-pitch pairs, for a total of 424 classes (i.e. 424 unique instrument-pitch pairs). We want to point out, however, that this is still a simplified problem compared to assisted orchestration. Even in the case of instrument-pitch pair classification, indeed, we would miss the dynamics of the note. To cope with this problem, in the orchestration phase, we quantize the probability functions generated by the models. When a network is given a target sound as input, it will attempt to apply the same classification rules, outputting a vector of the probabilities of each sample being in the target sound. Since the classes only encode instrument-pitch pairs and since we also need the dynamics, we quantize the probability function generated by the network into three echelons coresponding, respectively, to the dynamic levels \emph{pianissimo}, \emph{mezzoforte} and \emph{fortissimo} (see section \ref{sec:orchestration}). By taking the instruments and pitches that have the highest probability and by using quantized probabilities to retrieve dynamics, a full orchestrated solution can be created.  Figure \ref{fig:method} illustrates the described ideas.

@@

To create the input data for training the classifiers, we used the \emph{TinySOL} database. TinySOL is a subset of the Studio On Line (SOL) database created by IRCAM \cite{Cella2020b}. TinySOL contains 1,529 samples from 12 instruments. The instruments come from different orchestral families: strings, woodwinds, and brass. Each sample is one instrument playing a single note in the \emph{ordinario} playing style, with one of three dynamics: \textit{pp}, \textit{mf}, or \textit{ff} (for example \texttt{Flute-C4-pp} or \texttt{Clarinet-D5-mf}). The instruments and ranges over which they were recorded are summarized in table \ref{tab:ranges}.

For a given number of instruments $N$, each input to our model is a combination of $N$ TinySOL samples chosen among an orchestra of 10 instruments. The data is generated by selecting $N$ random TinySOL samples, leading to a variety of instruments, pitches, and dynamics; we did not allow the same instrument to be chosen more than three times in order to ensure variety in the mixtures. Then the chosen samples are combined to be played simultaneously and normalized by the number of instruments. The resulting combination has a sample rate of $44100$Hz and is padded or trimmed to be exactly 4 seconds long.

We then computed the Mel spectrogram of the combination to be the features input to our models. We generated the Mel spectrogram using an FFT hop length of 2048 samples (the window of each FFT was $46$ms long), and a number of Mel bins equal to 128. Therefore, the Mel features fed to the model were matrices of size $128\times 345$. We used the Librosa package in Python to compute the features; more details on the exact computations can be found in \cite{mcfee15}. The choice of the hop length was made by doing a compromise between the amount of information extracted by each FFT window, and the ability to capture temporal changes in the sound, assuming that musically relevant changes do not occur in a time frame less than $10$ms.

The choice of using the Mel spectrogram as input features for classification models is common in music information retrieval \cite{McKinney2003} and can be considered to be an appropriate representation of sound and musical signals. Such setup proved to be successful in \cite{Salamon17}.

\begin{table}
\begin{center}
	\begin{tabular}{|c|c|c|}
	\hline
	\textbf{Instrument} & \textbf{Abbreviation} & \textbf{Range} \\
	\hline
	Violin & Vn & G3-E7\\
	Cello & Vc & C2-C6\\
	Viola & Va & C3-C7\\
	Trumpet in C & TpC & F\#3-C6\\
	Trombone & Tbn & A\#0;A\#1-C5\\
	Oboe & Ob & A\#3-A6\\
	Horn & Hn & G1-F5\\
	Flute & Fl & B3-D7\\
	Clarinet in B$\flat$ & ClBb & D3-G6\\
	Contrabass & Cb & E1-C5\\
	Bass Tuba & BTb & F\#1-F4\\
	Bassoon & Bn & A\#1-D\#5\\
	\hline
	\end{tabular}
\caption{Table showing the pitch ranges present in the TinySOL database.\label{tab:ranges}}
\end{center}
\end{table}

@@

In order to get a better sense on the complexity of the problem, we tested three baseline classifiers: support vector machine (SVM), random forest (RF), and K-nearest neighbors (KNN). We used the implementations provided in the \emph{scikit-learn }library for Python \cite{scikit-learn}. More specifically, for SVM we used a non-linear RBF kernel and for RF we set the maximum depth of each tree to be 15.  All of the baseline experiments used 50,000 generated samples with a train-test split of 60/40. Each sample was made by a combination of one to ten instruments and was four seconds in length.

In this case, differently from the neural models, the features used are the MFCCs of the resulting combination; we chose to use MFCCs for this setting, instead of the Mel spectrogram, to have a lower number of features, that is more manageable by parametric classifiers. We found SVM to have the highest accuracy of the three classifiers across all experiments.

The complete problem of classification of the pairs instrument-pitch has 424 total classes. This problem is very difficult for parametric classifiers, so we initially switched to the simpler problem of classifying only the instruments and not the pitch. This had the benefit of both reducing the number of classes and increasing the number of samples per class. We found that SVM was able to very accurately identify the instrument given an input that had only one instrument present; for this case the accuracy was 99.8\%. However, as soon as multiple instruments were present in the input, the accuracy dropped significantly. With two instruments, accuracy was 55.4\%, with three it was 19.6\%. KNN performed significantly worse than SVM, so we did not attempt any further testing with it.

@@

We then performed this same experiment with three instruments having their pitch class identified. Flute, Oboe, and Violin reached an accuracy of 11.1\%, and Bass Tuba, Trumpet, and Trombone was 0.5\%. As we increased the number of instruments whose pitch classes was being identified, the accuracy continued to drop. For classifying the pitch class of four instruments (Oboe, French Horn, Violin, and Flute) the accuracy was 2.7\%.

This was still a simplified version of the problem, as we were identifying only the pitch class of a few instruments. However, the parametric classifiers were unable to achieve accurate results as the number of instruments increased. Therefore, we did not attempt, with parametric classifiers, the full setting of the problem in which individual pitches are classified for all instruments, and instead turned to our neural models.

@@

Following the first three convolutional layers, there is an LSTM layer which outputs 32 matrices. After the LSTM layer, there is a final convolutional layer yielding a tensor of dimensions $32\times 8 \times 21$. We flatten the outputs and feed them into a fully connected layer with Dropout, then another another fully connected layer. Finally, the sigmoid function is applied to the final layer. Since each class is independent, we are able to take the sigmoid activation and use binary classification for each class. The model architecture is shown in Figure \ref{cnn_lstm}.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../ISMIR_2020/figs/CNN_LSTM_diagram.png}
	\caption{Diagram of the CNN with LSTM architecture. \label{cnn_lstm}}
\end{figure}

@@

\begin{figure}
  \center{
  \includegraphics[width=0.8\textwidth]{../ISMIR_2020/figs/CNN_vs_ResNet.png}}
  \caption{Best overall accuracy for CNN with LSTM (50 epochs, 200k samples per epoch) and ResNet (20 epochs, 400k samples per epoch) depending on the number of instruments in the combinations used for training. \label{cnn_vs_resnet}}
\end{figure}

@@

\begin{figure}
  \centering
  \begin{subfigure}{.52\textwidth}
    \centering
    \includegraphics[width=0.9\linewidth]{../ISMIR_2020/figs/Acc_vs_N_CNN.png}
    \caption{CNN with LSTM}
    \label{best_acc_cnn}
  \end{subfigure}%
  \begin{subfigure}{.52\textwidth}
    \centering
    \includegraphics[width=0.9\linewidth]{../ISMIR_2020/figs/Acc_vs_N_ResNet.png}
    \caption{ResNet}
    \label{best_acc_resnet}
  \end{subfigure}
  \caption{Plot showing per instrument accuracies for CNN with LSTM and ResNet depending on the number of samples present in the combinations}
  \end{figure}

@@

In order to test our models for orchestration, we used 15 targets from the Orchidea distribution. These targets represent a variety of signal types but are mostly static, in the sense that the harmonic average across time is a good representation of the sample. Some of the targets were made of instrumental samples: a sum of oboe and bassoon notes, single bassoon and bass clarinet notes, two multiphonics of bassoon and two symphonic chords. Other targets were recordings that were not instrumental: bell sounds, car horn, gong, screaming voice, wind harp, the attack of a brass instrument, and the recording of a boat docking.

@@

In order to have a better comparison, we did not allow Orchidea to use any of the advanced features: we did not apply any symbolic constraints or harmonic analysis and we forced it forced to use all 10 instruments in each solution. This creates a more fair comparison, since our models are unable to create constrained or sparse solutions.

@@

@@

We calculated the distance between the target samples and our orchestrated solutions. We then orchestrated the same targets with Orchidea and calculated the distance for Orchidea's solutions. A comparison of these results is in Table \ref{orch_eval}. While our model is not able to outperform Orchidea, it shows consistent results. We find that the CNN and ResNet give similar accuracies during training, but perform differently when tasked with orchestrating targets. Overall, CNN seems to better emulate the timbre in its orchestrations, where ResNet is better for recreating the harmonic content of the target. You can listen to the targets and orchestrated solutions from Orchidea, ResNet, and the CNN with LSTM at \url{https://dzluke.github.io/DeepOrchestration/}.
